Data Analysis

### 2022-04-08 02.get_person_stats.Rmd
updating analysis

  # combine types
  works_df$our_type <- works_df$type
  works_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", works_df$our_type)

@@

works_df <- do.call(bind_rows, author_works) %>% select(-external_ids_external_id)
works_df$ORCID <- rep(names(author_works), lapply(author_works, nrow))
write.csv(works_df, "ORCID_works.csv", row.names = F)

>>>>

@@

works_df <- do.call(bind_rows, author_works) %>% select(-external_ids_external_id)
works_df$ORCID <- rep(names(author_works), lapply(author_works, nrow))
works_df <- works_df %>% 
      dplyr::mutate(last_modified_date_value = 
                      anytime::anydate(last_modified_date_value/1000))

write.csv(works_df, "ORCID_works.csv", row.names = F)

### 2022-04-08 03.data_analysis.Rmd
updating analysis

```{r}
library(dplyr)
library(bib2df)
library(rio)
```

@@

```{r}
o_works <- import("ORCID_works.csv")
o_ed <- import("ORCID_ed.csv")
o_job <- import("ORCID_job.csv")

s_works <- import("") 
s_info <- import("")
```

@@

@@

>>>>

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)

#### fix sau chins paper ####
```

@@

```{r}
id_list <- import("test_utf8.xlsx")

o_works <- import("ORCID_works.csv")
o_ed <- import("ORCID_ed.csv")
o_job <- import("ORCID_job.csv")

s_works <- import("scholar_works.csv") 
s_info <- import("scholar_info.csv")
```

@@

```{r}
o_works$publication_date_year_value[o_works$publication_date_year_value < 1920] <- NA

table(o_works$type)

# combine types ####see issues here #### 
# works_df$our_type <- works_df$type
# works_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", works_df$our_type)

o_works_summary <- o_works %>% 
  group_by(ORCID) %>% 
  summarize(o_career_1_pub = 2022 - min(publication_date_year_value, na.rm = T),
            o_total_pub = n())

s_works_summary <- s_works %>% 
  group_by(scholar) %>% 
  summarize(s_career_1_pub = 2022 - min(year, na.rm = T),
            s_total_pub = n())
####citations??####

####see issues here####
o_ed_summary <- o_ed %>% 
  group_by(ORCID) %>% 
  summarize(o_career_1_degree = 2022 - min(education_summary_end_date_year_value, na.rm = T))

# create a table that's ORCID, job, education, year for each year within bib 2013 to 2022

@@

## Merge Information Back

```{r}
merged_df <- long_bib %>% 
  left_join(
    (id_list %>% select(first, last, ORCID, scholar)), 
    by = c("first" = "first", "last" = "last")
  ) %>% 
  left_join(
    o_works_summary, 
    by = c("ORCID" = "ORCID")
  ) %>% 
  left_join(
    s_works_summary,
    by = c("scholar" = "scholar")
  ) %>% 
  left_join(
    o_ed_summary,
    by = c("ORCID" = "ORCID")
  ) %>% 
  left_join(
    (s_info %>% select(scholar, h_index, i10_index)),
    by = c("scholar" = "scholar")
  )

## Journal Information

```{r}
table(bibs$JOURNAL)
table(bibs$KEYWORDS)

## Over Time
